Dynamic Topic Modeling for Voice Dialogues

### 2024-05-21 paper/main.tex
update segmetation exps

\section{Text clustering}

The input data at this stage are dialogues divided into separate utterances of the participants ${ut_1, ut_2, \dots, ut_n}$.
At this stage, experiments will be conducted using the encoder model for the Utterance-Coherence Scoring algorithm. 
In addition, algorithms for the time of model inference will be performed throughout the pipeline to select the fastest solution.

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c |} 
        \hline
        \multirow{2}{*}{models} & \multicolumn{3}{| c |}{Tiage} &  \multicolumn{3}{| c |}{SuperDialseg}  \\
        \cline{2-7}
         & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg & 0.492 & 0.508 & 0.181 & 0.497 & 0.501 & 0.359 \\
        GraphSeg & 0.462 & 0.466 & 0.239 & 0.496 & 0.515 & 0.238 \\
        TextTilling & 0.469 & 0.488 & 0.204 & 0.446 & 0.458 & 0.378 \\
        TeT + BERT & 0.425 & 0.439 & 0.285 & 0.522 & 0.531 & 0.201 \\
        \hline\ 
        Our solution+BERT-NSP & Pk & wd & f1 & Pk & wd & f1 \\ 
        Our solution+BERT-CLS & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
        \multirow{2}{*}{models} & \multicolumn{3}{| c |}{AMI} & \multicolumn{3}{| c |}{ICSI} \\
        \cline{2-7}
        & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg & 0.885 & 0.792 & 0.0641 & 0.762 & 0.730 & 0.109 \\
        GraphSeg & Pk & wd & f1 & Pk & wd & f1 \\
        TextTilling & Pk & wd & f1 & Pk & wd & f1 \\
        TeT + BERT & Pk & wd & f1 & Pk & wd & f1 \\ 
        \hline
        Our solution+BERT-NSP & Pk & wd & f1 & Pk & wd & f1 \\ 
        Our solution+BERT-CLS & Pk & wd & f1 & Pk & wd & f1 \\  
        \hline
    \end{tabular}
    \captionof{table}{Dialogue segmentation experiments}
\end{center}

>>>>

\section{Dialogue Segmenentation}

The input data at this stage are dialogues divided into separate utterances of the participants ${ut_1, ut_2, \dots, ut_n}$.
At this stage, experiments will be conducted using the encoder model for the Utterance-Coherence Scoring algorithm.

\begin{center}
    \begin{tabular}{ | c | c | c | c | c | c | c | c |} 
        \hline
        \multirow{2}{*}{models} & \multicolumn{3}{| c |}{Tiage} &  \multicolumn{3}{| c |}{SuperDialseg}  \\
        \cline{2-7}
         & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg & 0.492 & 0.508 & 0.181 & 0.497 & 0.501 & 0.359 \\
        GraphSeg & 0.462 & 0.466 & 0.239 & 0.496 & 0.515 & 0.238 \\
        TextTilling & 0.469 & 0.488 & 0.204 & \cellcolor{green!20} 0.446 & \cellcolor{green!20} 0.458 & \cellcolor{green!20} 0.378 \\
        TeT + BERT & \cellcolor{green!20} 0.425 & \cellcolor{green!20} 0.439 & \cellcolor{green!20} 0.285 & 0.522 & 0.531 & 0.201 \\
        \hline\ 
        CohScoring+BERT-NSP & 0.4465 & 0.4575 & 0.267 & 0.5071 & 0.5219 & 0.205 \\ 
        CohScoring+BERT-NSP fine-tune & \cellcolor{green!40} 0.3981 & \cellcolor{green!40} 0.4018 & \cellcolor{green!40} 0.32 & \cellcolor{green!40} 0.4361 & \cellcolor{green!40} 0.44510 & \cellcolor{green!40} 0.285 \\ 
        \hline
        \multirow{2}{*}{models} & \multicolumn{3}{| c |}{AMI} & \multicolumn{3}{| c |}{ICSI} \\
        \cline{2-7}
        & Pk $\downarrow$ & wd $\downarrow$ & f1 & Pk $\downarrow$ & wd $\downarrow$ & f1 \\ 
        \hline
        GreedySeg & 0.885 & 0.792 & 0.3641 & 0.762 & 0.730 & 0.309 \\
        GraphSeg & 0.875 & 0.750 & 0.422 & 0.810 & 0.756 & 0.275 \\
        TextTilling & Pk & wd & f1 & Pk & wd & f1 \\
        TeT + BERT & Pk & wd & 0.443 & Pk & wd & 0.158 \\ 
        \hline
        CohScoring+BERT-NSP & \cellcolor{green!20} 0.6447 & \cellcolor{green!20} 0.7394 & \cellcolor{green!20} 0.551 & \cellcolor{green!20} 0.6148 & \cellcolor{green!20} 0.6731 & \cellcolor{green!20} 0.779 \\ 
        CohScoring+BERT-NSP fine-tune & \cellcolor{green!40} 0.5854 & \cellcolor{green!40} 0.6032 & \cellcolor{green!40} 0.587 & \cellcolor{green!40} 0.5842 & \cellcolor{green!40} 0.5932 & \cellcolor{green!40} 0.815 \\ 
        \hline
    \end{tabular}
    \captionof{table}{Dialogue segmentation experiments}
\end{center}
